### 2020-01-31 wuhan.tex
code
merge-pull

We strongly emphasize the need for accurate characterization of the transmission chains via contact tracing and better statistical framework for inferring generation-interval distributions from such data \citep{britton2019estimation}.
A combined effort between healthcare workers and modelers in this direction will be crucial for predicting the course of an epidemic and controlling it.

>>>>

We strongly emphasize the value of attention to accurate characterization of the transmission chains via contact tracing and better statistical framework for inferring generation-interval distributions from such data \citep{britton2019estimation}.
A combined effort between public-health workers and modelers in this direction will be crucial for predicting the course of an epidemic and controlling it.
%% \jd{Leave the medical folks out; we don't want to ad
